%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%                                                                 %
%                         ACKNOWLEDGEMENT                         %
%                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
 
\chapter*{Acknowledgments}

My supervisors, Prof. Dr. Paul Pl\"{o}ger, Prof. Gerhard Lakemeyer, Ph.D. and Dipl. Inform. Tim Niemueller, were instrumental in shaping the direction of the thesis. I would like to thank Prof Pl\"{o}ger for introducing me to topic of probabilistic machine learning, Tim for having trust on me and providing me the thesis topic and Prof Lakemeyer for allowing to work in his department. Special thanks to Iman Awaad for the helping me shaping the proposal of the thesis.

I would like to thank Santosh George Thoduka, Shehzad Ahmed, Daniel Vázquez and Tan Chun Kwang for all the uncountable discussions in lab,
 all of which has helped me in gaining better ``knowledge" about my thesis. 
Also would thank Frederik Zwilling for helping me with the setting up FAWKES and patiently answering all my queries. 

I would like to acknowledge the STRANDS project for providing the datasets used in the thesis. 
 
I would also thank Dr. Jaakko Luttinen for providing the library BayesPy, and solving all my issues with the library. 

Thanks also to Santosh George Thoduka and Tan Chun Kwang for proof-reading my report at the last minute.

On a more personal note, I would like to thank my family for their support during my 2 year adventure in the MAS.